An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-02-15 EconGrowth.Rnw
Added a function that creates country rows for the parameters graphs for LINEX.

@@

\begin{equation} \label{eq:LINEX_model}
  y = e \: \mathrm{exp} \left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)       \right]
\end{equation}

@@

Figure \ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions with historica data.

<<LINEX_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="LINEX results.", eval=TRUE>>=
createLinexLatticeGraph()
@

>>>>

###########################################
# Creates a number of rows in a data.frame that contain information 
# about the coefficients of a LINEX model for countryName and energyType
# Each parameter has its own row with confidence intervals.
# The country name is in a column. Which parameter is involved is
# also in a column.
# 
# The return type is a data.frame.
##
linexCountryRowsForParamsGraph <- function(countryName, energyType){
  #Create three rows, one for each parameter. Each row is a data.frame so that it is plottable!
  dataLINEX <- linexData(countryName, energyType)
  a_0Row <- data.frame(country = countryName, 
                          parameter = "a_0", 
                          lowerCI = dataLINEX["-95% CI", "a_0"], 
                          value = dataLINEX["LINEX", "a_0"], 
                          upperCI = dataLINEX["+95% CI", "a_0"])
  c_tRow <- data.frame(country = countryName, 
                         parameter = "c_t",
                         lowerCI = dataLINEX["-95% CI", "c_t"],
                         value = dataLINEX["LINEX", "c_t"],  
                         upperCI = dataLINEX["+95% CI", "c_t"])
  table <- rbind(a_0Row, c_tRow)
  return(table)
}

@@

\begin{equation} \label{eq:LINEX_model}
  y = e \: \mathrm{exp} \left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right) \right],
\end{equation}

@@

Figure \ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions with historical data.

<<LINEX_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="LINEX results.">>=
createLinexLatticeGraph()
@
